Significance testing with forward stepwise and grouped forward stepwise model selection

### 2013-09-27 paper/paper.tex
Added code for categorical designs

\endlocaldefs

@@

>>>>

\newcommand{\V}{\mathcal{V}}\endlocaldefs
\newcommand{\K}{\mathcal{K}}

@@

For the sake of completeness this appendix provides full derivations
of closed forms for the quantities required to compute our
statistic. We require two facts from \cite{tests:adaptive}

A point $\eta \in \K$ maximizes $f_\eta$ over a convex
set $\K$ if and only if the following conditions hold: 
\begin{equation}
\label{eq:maxcond}
\grad f_{|T_{\eta}\K} = 0, \quad
\tf^{\eta}_{\eta} \geq \V^+_{\eta}, \quad
\tf^{\eta}_{\eta} \leq \V^-_{\eta}, \quad \text{and} \quad
\V^0_{\eta} \leq 0.
\end{equation}
The same equivalence holds true even when $\K$ is only locally
convex.
